The globular cluster system of the Auriga simulations

### 2019-08-02 AurigaGCS.tex
Move relevant/used figures to separate folder
Done processing SW's feedback

\usepackage{todonotes}
\graphicspath{{img/}}   % Set image path

@@

C11 and CR16 present a uniform set of spectroscopic observations calibrated
on the Milky Way GCS of the inner $1.6^\circ~({\sim}21)$~kpc that
is believed to be 94\% complete. GCs in the outer stellar halo, up to
$R_{\text{proj}}\sim150$~kpc, are observed in the Pan-Andromeda Archaeological
Survey \citep[PAndAS, ][hereafter H14]{2014MNRAS.442.2165H}, but see also
\citet{2014MNRAS.442.2929V} and \citet{2019MNRAS.484.1756M}. H14 presents the
discovery of 59 new GCs and publishes updates to RBC~5. The work of H14 is
incorporated in the latest public release\footnote{Last revised 23 Sep 2015, see
\url{https://www.cfa.harvard.edu/oir/eg/m31clusters/M31_Hectospec.html}}
of the C11 dataset, further revised by CR16. It seems that CR16 is the most
recent aggregated dataset of M31's GCS that contains properties of interest
for our study as it contains GCs in the inner region and in the outer halo. The
relevant fields in the CR16 dataset that we use are the age, metallicity, and the
mass-estimate\footnote{The authors assumed $M/L_V = 2$ independent of [Fe/H]}.

\subsection{Age-estimates}
Figure~\ref{fig:MW-M31-age} shows a histogram of the age-estimates of the $55$
MW GCs in V13 and $88$ GCs in M31 for which age-estimates are available in CR16.
The mean age of the MW GCs in this data set is $11.9 \pm 0.1$~Gyr and the 
dispersion is $0.8$~Gyr. Furthermore, only one of the 55 GC age-estimates is
below $10$~Gyr. The M31 GCS has a mean age of $11.0 \pm 0.2$~Gyr with a dispersion 
of $2.2$~Gyr, and $24$ GCs have age-estimates below $10$~Gyr with a minimum age 
of $4.8$~Gyr. Based on these data, we find that the age distributions of the MW 
and M31 GCS's are not statistically consistent. Moreover, the Milky Way appears 
to host a globular cluster system that is somewhat older than the Andromeda galaxy,
which is somewhat surprising given that M31 is generally considered to be earlier
type than the MW meaning that an older stellar population would naively be expected
. However, we do caution that both data sets are incomplete and the age 
measurements have large uncertainties (of $1-2$~Gyr). On the other hand, the 
magnitude of the uncertainty is insufficient to explain the low-age tail in M31.

\begin{figure}
    \includegraphics[width=\columnwidth]{{MW_M31_Age_Histogram-trim}.png}
    \caption{
        Age distribution of 55 GCs in the MW
        \citep[data from][]{2013ApJ...775..134V} and 88 GCs
        in M31 \citep[data from][]{2016ApJ...824...42C}.
        \label{fig:MW-M31-age}
    }
\end{figure}

\subsection{Total GC mass in metallicity-radial space}
\label{sec:observations_FeHRgc}
We show the two-dimensional mass-weighted metallicity-radial distribution of the
MW (M31) GCS in the top (bottom) panel of Figure~\ref{fig:observations_FeHRgc}. Both
quantities are readily available in H96e10 (assuming $R_{\odot}=8.0$~kpc), but
the galactocentric radius of GCs in M31 is not available in CR16. Therefore we
follow \citet[][Sec.~4.1]{2019arXiv190111229W} to calculate the projected radius
$R_{\text{proj}}$ from the observed positions, adopting M31's central position
from the NASA Extragalactic Database\footnote{\url{https://ned.ipac.caltech.edu/}}
$(\alpha_0, \, \delta_0) =
(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$
and distance $D_{\text{M31}} = 780$~kpc \citep{2005MNRAS.356..979M,2012ApJ...758...11C}
We calculate $R_{\text{GC}}$ as `average deprojected distance`
$R_{\text{GC}} = R_{\text{proj}} \times (4/\pi)$. The observations indicate that
no GCs with high metallicities are to be expected at large radii (the three bins
in the upper right corner, both for MW and M31), and relatively few GCs at large
radii in general ($R_{\text{GC}} > 30$~kpc; right column: $11$ GCs or 7.3\% in
the MW and $17$ or 4.6\% in M31). Moreover, the M31 hosts more metal-rich 
([Fe/H]$ > -1$) GCs in each radial bin in comparison to the MW GCSs than what
would be expected when accounting for the fact that Andromeda hosts a larger GC 
system than the MW. Finally, given that both marginalized (i.e. the metallicity 
and radial) distributions are not statistically consistent, we find that the 
two-dimensional distributions are also not consistent. More generally, the GC
systems of the Milky Way and that of Andromeda both differ significantly. We 
compare these observations to the Auriga simulations later on in 
Sec.~\ref{sec:results_FeHRgc}.

@@

\section{Results}
\label{sec:results}
We define GC candidates in the Auriga simulations as all star particles older
than $10$~Gyr based on the age distribution of the MW GCS (Figure~\ref{fig:MW-M31-age}),
and following the analysis of \citet{2017MNRAS.465.3622R}.

Trough out our analysis we compare the distributions of three subsets of star
particles: \emph{old stars} (age $>10$~Gyr, or GC candidates), \emph{old insitu}
stars (defined as those bound to the most-massive halo/subhalo in the first
snapshot that the particle was recorded), and \emph{old accreted} star particles
(those that have formed ex-situ and are bound to the most-massive halo/subhalo
at $z=0$). For comparison we also include the results for \emph{all stars} (when
no additional selection criterion is applied to the star particles). We consider
the metallicity distribution in Sec.~\ref{sec:results_FeH}, the distribution of
galactocentric radii in Sec.~\ref{sec:results_Rgc}, and the combination of both
in Sec.~\ref{sec:results_FeHRgc}.

\subsection{Metallicity distribution}
\label{sec:results_FeH}
We investigate whether the star formation model implemented in Auriga produces
metallicity distributions consistent with the MW and M31 GC systems, and whether
the subgrid generates sufficient total mass at metallicities typical for the
MW and M31 GCS's. To visually inspect the former we show the normalized metallicity 
distribution of three specific Auriga galaxies in Figure~\ref{fig:Au4-10and21_FeH}
in comparison to the MW and M31 [Fe/H] distributions.

\begin{figure*}
    \includegraphics[width=\columnwidth]{{Au4-10_FeH_cleaner-trim}.png}
    \includegraphics[width=\columnwidth]{{Au4-4_and_Au4_21_FeH-trim}.png}
    \caption{
        \emph{Left:} Metallicity distribution of Au4-10 (bottom panel). We show
        the GG candicates in green. We split the GC candidates into two
        subpopulations, those that have formed insitu (blue), and those that have
        been accreted (red). The dotted green line shows all star particles.
        The solid purple (magenta) line in the top panel shows the GC system
        of the MW (M31). \emph{Right:} Au4-4 (bottom), and Au4-21 (top).
        \label{fig:Au4-10and21_FeH}
    }
\end{figure*}
We select \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the
resolution level (4) and halo number (10, indicating which set of initial
conditions was used the run).}, \mbox{Au4-21}, and \mbox{Au4-4} to show the
distributions of three individual simulation runs that we consider representative
for specific behaviour, and to highlight that different runs could give rise to 
different distributions. We plot the age-selected GC candidates in green, those
that are accreted in red, and the insitu subpopulation in blue. The top 
half of the left figure shows the MW (M31) GC system in purple (magenta), where 
we overplot a double Gaussian for the MW GCS (the purple dashed lines) by 
adopting literature values of the mean $\mu$ and standard deviation $\sigma$ of 
the metal-rich and metal-poor subpopulations \citep[][p. 38]{Harris2001}.

We find that the age cut, on average, lowers the mean metallicity from $0.0$ to
$-0.6$. Furthermore, the old accreted stars generally have lower mean metallicities
than the old insitu stars with differences of roughly ${\sim}0.3$ for the majority 
of the simulation runs. This behaviour can be seen in \mbox{Au4-21}, while a 
slightly larger difference of ${\sim}0.5$ dex is seen for \mbox{Au4-10} (as plotted), 
\mbox{Au4-16}, \mbox{Au4-17}, \mbox{Au4-18} and \mbox{Au4-22}. However, this trend 
is reversed for \mbox{Au4-1} and \mbox{Au4-4} for which the old insitu population 
has a lower mean metallicity instead. We caution that \mbox{Au4-1} is undergoing
a major merger at redshift zero and note that we find $\mu = -1.51 \, ({-0.74})$ 
for the old insitu (accreted) although the former consists of only $1019$ 
particles ($1.3$\% of all GC candidates, and with a total mass of 5e7 M\Sun). 
For \mbox{Au4-4}, ${10.8}$\% of the GC candidates is classified as insitu (compared 
to insitu fractions of ${40-80}$\% for other haloes). Overall we find that the 
simulations produce (sub)populations of GC candidates that are
more metal-rich than the MW and M31 GC systems. Moreover, none of the simulations
has a population of GC candidates with a bimodal metallicity distribution
(the green curves).

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_mu_sigma-trim}.png}
    \caption{
        First vs second central moment of the Auriga L4 metallicity distributions.
        Each cross (for a given colour) represents one simulation. The green (blue)
        [red] crosses show the values calculated using the old (old insitu)
        [old accreted] star particles. Green triangles indicate that all stars
        were used. The purple (magenta) cross denotes our calculation using all
        MW (M31) observations (which would be appropriate for a unimodal
        distribution). The black solid (open) dots indicate the literature values
        of a bimodal Gaussian fit to the data \citep[values from][p. 38]{1998gcs..book.....A},
        showing the metal-rich (metal-poor) component of the MW.
        \label{fig:FeH_mu_sigma}
    }
\end{figure}

We show the mean metallicity and standard deviation of all thirty Auriga L4 haloes
in Figure~\ref{fig:FeH_mu_sigma} to show the behaviour for the full set of Auriga
galaxies. The green crosses are to be compared to the purple (magenta) cross, 
which shows the mean value of all MW (M31) GCs. In addition, we show the metal-rich 
(metal-poor) population of the MW GCS using a solid (open) dot. We caution that
these literature values result from individual Gaussian fits to sub sets of the 
observational data cut at [Fe/H]~$= -1$. We do not include corresponding data 
points calculated using such an artificial cut for the simulated star particles.
Having said that, we do find it interesting that the mean metallicities of the 
old insitu populations appear roughly consistent with that of the metal-rich 
population of the MW although the simulations show larger dispersions. The latter 
could simply be caused by the hard separation of the data into two groups, which 
means the range is smaller and the resulting dispersion could be lower. With 
regard to the M31 GCS, we are uncertain whether definitive consensus is reached
concerning uni- bi- or trimodality in the [Fe/H] distribution, but CR16 argues 
that the data, after removal of younger objects due to improved age classification, 
hints at three populations separated at [Fe/H]~$>-0.4$ and [Fe/H]~$ < 1.5$. None 
of the Auriga sub sets has a mean value that offers much hope that the simulated 
distribution is consistent with the lowest metallicity group in the M31 GCS. This 
is also true for the metal-poor population of the MW with a mean value of $-1.6$.
The main take-away from this plot, again, is that all Auriga L4 galaxies have
metallicity distributions with (much) larger mean values than what is observed
for the MW and M31 GCS, and that we systematiclly find lower mean metallicities
for the accreted GC candidates than for those that have formed in situ.

Finally, we test the null hypothesis that MW (M31) and the GC candidates (all, insitu, and
accreted) are drawn from the same underlying distribution by calculating the KS
test statistic (i.e. six KS tests per simulation). We reject $H_0$ at the 100.00~\%
confidence level for virtually all subsets of all simulations, both for MW and M31,
except when comparing the old accreted stars of \mbox{Au4-10} to the MW GCS. In this
case we still reject $H_0$ with, but with $\leq 98.68$~\% confidence. When comparing
to the M31 GCS, the `best' matches are the old accreted subpopulations of \mbox{Au4-13},
\mbox{Au4-15}, and \mbox{Au4-17} ($H_0$ rejected with $\leq$ 99.82~\% confidence, 99.95~\%,
and 98.32~\%). Here we find that the cumulative distributions are more or less
similar up to [Fe/H]~$-0.5$, above which the simulations yield higher number
counts which drives the KS test statistic over the critical values. This affirms
our finding that the simulations produce GC candidates that are more metal-rich
than the MW (M31) GCS. The main reasons that $H_0$ is rejected with such
high confidence are under-production of old stars with [Fe/H]~$\leq$~-1.5,
and over-production of stars with [Fe/H]$\geq$~-0.5.

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
We now turn to the second goal, which is to see whether sufficient total mass in 
GC candidates produced by the Auriga simulations. To answer this question we plot
a mass-weighted metallicity distribution in Figure~\ref{fig:FeH}. We show the 
median (coloured lines) for all thirty Auriga L4 haloes with the $1\sigma$ 
interval around it (shaded regions, which shows the scatter between runs that 
have different initial conditions, thus, have unique merger histories). We chose 
to aggregate the data to indicate general trends that we find when the GC candidates 
are split up according to birth location, rather than selecting typical examples 
of individual (simulated) galaxies. Once again we notice that the peak metallicity 
shifts down from $0$ to $-0.6$ for old stars (green solid) compared to all stars 
(green dotted), and we learn that the mass at the peak lowers by roughly one dex. 
The mass budget of the old stars is dominated by the old insitu population (blue 
solid) below [Fe/H]~=~$-1$, and by the old accreted stars (red solid) above this 
value. We show the MW (M31) GCS in purple (magenta) and notice that the difference 
between the MW and M31 distributions is substantially larger than the scatter
between different Auriga galaxies, particularly around [Fe/H]~$=-1$. In addition, 
Andromeda does host (a hand full) GCs with [Fe/H]~$< -2.5$ as well as GCs with 
[Fe/H]~$ > 0$ while the Milky Way does not.

We show the ratio of the  simulated to the observed profiles in the middle (bottom) 
panel. This mass excess can be thought of the `mass budget' that the Auriga GC 
candidates can `afford to lose' due to a combination of smaller than unity bound
cluster formation efficiencies combined with a Hubble time of dynamical evolution,
while still producing sufficient mass at the right metallicities. In particular,
the cluster formation efficiency would have to linearly decrease with decreasing 
metallicity for Auriga GC candidates to produce a population of GC candidates 
that is consistent with the MW. For the GC candidates in M31 we find a constant 
mass excess up to $-0.9$, above which the simulations produce a higher mass excess 
with increasing metallicity. If dynamical evolution is not expected to more 
efficiently disrupt GCs of higher metallicity, then we would find that the 
efficiency to form bound star clusters would have to decrease with increasing 
metallicity.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{Rgc_mu_sigma-trim}.png}
    \caption{
        Mean and standard deviation of the radial distribution of star particles
        in each of the thirty Auriga L4 haloes compared to the MW (M31) GCS
        shown in purple (magenta).
        \label{fig:Rgc_mu_sigma}
    }
\end{figure}
We repeat the analysis of the previous subsection for the distribution of
galactocentric radius instead of metallicity. We look for general trends present
in all Auriga L4 galaxies. Figure~\ref{fig:Rgc_mu_sigma} shows the mean and 
standard deviation of the radial distribution of star particles in all Auriga L4 
simulations. We notice that the old insitu populations are more centrally 
distributed, whereas the old accreted subsets have a larger radial extent. This 
is not surprising because the classification of in situ requires star particles 
to have formed within the virial radius, thus they could naturally be expected 
to end up at small galactocentric radii. Accreted star particles, on the other 
hand, have formed in another (sub)halo beyond the virial radius, thus, would 
first have to migrate inwards in order to populate the innermost radii. Moreover, 
we notice that the dispersion increases with increasing mean value of the radial 
distribution as may be expected for a non-negative quantity. The purple (magenta)
cross indicates the values for the MW (M31) GCS, which are to be compared to the
green crosses. The MW GCS lies roughly within the range of values seen for the 
radial distributions produced by the Auriga simulations, whereas the mean of M31
is larger and closer to typical mean values of the accreted GC candidates in
the Auriga simulations. The larger radial extend of the M31 GCS is generally
believed to hint at a more accretion-dominated origin of the GCS, and may reflect
a richer accretion history of the galaxy in comparison to the Milky Way.

>>>>

\usepackage{todonotes}
\graphicspath{{figures/}}   % Set figure path

@@

C11 and CR16 present a uniform set of spectroscopic observations calibrated
on the Milky Way GCS of the inner $1.6^\circ~({\sim}21)$~kpc that
is believed to be 94\% complete. GCs in the outer stellar halo, up to
$R_{\text{proj}}\sim150$~kpc, are observed in the Pan-Andromeda Archaeological
Survey \citep[PAndAS, ][hereafter H14]{2014MNRAS.442.2165H}, but see also
\citet{2014MNRAS.442.2929V} and \citet{2019MNRAS.484.1756M}. H14 presents the
discovery of 59 new GCs and publishes updates to RBC~5. The work of H14 is
incorporated in the latest public release\footnote{Last revised 23 Sep 2015, see
\url{https://www.cfa.harvard.edu/oir/eg/m31clusters/M31_Hectospec.html}}
of the C11 dataset, further revised by CR16. It seems that CR16 is the most
recent aggregated dataset of M31's GCS that contains properties of interest
for our study as it contains GCs in the inner region and in the outer halo. The
relevant fields in the CR16 dataset that we use are the age, metallicity, and the
mass-estimate\footnote{The authors assumed $M/L_V = 2$ independent of [Fe/H]}.
Radii are calculated from RA and DEC, further discussed in Sec.~\ref{sec:Rgc}.

\subsection{Age-estimates}
The top panel of Figure~\ref{fig:MW-M31-age-Rgc} shows a histogram of the age-estimates
of the $55$ MW GCs in V13 and $88$ GCs in M31 for which age-estimates are available
in CR16. The mean age of the MW GCs in this data set is $11.9 \pm 0.1$~Gyr and the 
dispersion is $0.8$~Gyr. Furthermore, only one of the 55 GC age-estimates is
below $10$~Gyr. The M31 GCS has a mean age of $11.0 \pm 0.2$~Gyr with a dispersion 
of $2.2$~Gyr, and $24$ GCs have age-estimates below $10$~Gyr with a minimum age 
of $4.8$~Gyr. Based on these data, we find that the age distributions of the MW 
and M31 GCS's are not statistically consistent. Moreover, the Milky Way appears 
to host a globular cluster system that is somewhat older than the Andromeda galaxy,
which is somewhat surprising given that M31 is generally considered to be earlier
type than the MW meaning that an older stellar population would naively be expected.
However, we do caution that both data sets are incomplete and the age 
measurements have large uncertainties (of $1-2$~Gyr). On the other hand, the 
magnitude of the uncertainty is insufficient to explain the low-age tail in M31.

\subsection{Radial distribution}
\label{sec:Rgc}
The bottom panel of Figure~\ref{fig:MW-M31-age-Rgc} shows the radial distribution
of the MW and M31 GCS. Both quantities are readily available in H96e10 (assuming
$R_{\odot}=8.0$~kpc), but the galactocentric radius of GCs in M31 is not available
in CR16. Therefore we follow \citet[][Sec.~4.1]{2019arXiv190111229W} to calculate
the projected radius $R_{\text{proj}}$ from the observed positions, adopting M31's
central position from the NASA Extragalactic 
Database\footnote{\url{https://ned.ipac.caltech.edu/}} $(\alpha_0, \, \delta_0) =
(0^{\text{h}}42^{\text{m}}44.35^{\text{s}}, \, +41^{\circ}16'08.63")$
and distance $D_{\text{M31}} = 780$~kpc \citep{2005MNRAS.356..979M,2012ApJ...758...11C}.
We calculate $R_{\text{GC}}$ as `average deprojected distance`
$R_{\text{GC}} = R_{\text{proj}} \times (4/\pi)$.

The solid lines show the distributions using all available data (because the
sky coordinates are known for each GC), while the subset for which age-estimates
are available is indicated using dotted lines. The latter shows a narrower range
of radii than the full data set: it appears that age-estimates are neither
available for the innermost ($<1$~kpc) GCs, nor for those beyond roughly twenty
kpc (the halo GCs). We compare both distributions of the full data set (solid 
lines) and find that the Milky Way has more GCs in the range $1-4$~kpc than M31
(when accounting for the larger number of total GCs in M31). Interestingly, both
distributions show a similar trend for $R_{\text{GC}} > 4$~kpc and host a 
subpopulation of halo GCs. However, both radial distributions are not 
statistically consistent due to substantial differences at intermediate radii.

\begin{figure}
    \includegraphics[width=\columnwidth]{{MW_M31_Age_Histogram-trim}.png}
    \includegraphics[width=\columnwidth]{{MW_M31_Rgc_Histogram-trim}.png}
    \caption{
        \emph{Top}: Age distribution of 55 GCs in the MW
        \citep[data from][]{2013ApJ...775..134V} and 88 GCs
        in M31 \citep[data from][]{2016ApJ...824...42C}.
        \emph{Bottom:} Distribution of galactocentric radius in the MW and M31.
        The dotted lines show the subset of data that also have age measurements
        (i.e. the same sample as used in the top panel).
        \label{fig:MW-M31-age-Rgc}
    }
\end{figure}

\subsection{Total GC mass in metallicity-radial space} \label{sec:observations_FeHRgc}
We show the two-dimensional mass-weighted metallicity-radial distribution of the
MW (M31) GCS in the top (bottom) panel of Figure~\ref{fig:observations_FeHRgc}. 
The observations indicate that
no GCs with high metallicities are to be expected at large radii (the three bins
in the upper right corner, both for MW and M31), and relatively few GCs at large
radii in general ($R_{\text{GC}} > 30$~kpc; right column: $11$ GCs or 7.3\% in
the MW and $17$ or 4.6\% in M31). Moreover, the M31 hosts more metal-rich 
([Fe/H]$ > -1$) GCs in each radial bin in comparison to the MW GCSs than what
would be expected when accounting for the fact that Andromeda hosts a larger GC 
system than the MW. Finally, given that both marginalized (i.e. the metallicity 
and radial) distributions are not statistically consistent, we find that the 
two-dimensional distributions are also not consistent. More generally, the GC
systems of the Milky Way and that of Andromeda both differ significantly. We 
compare these observations to the Auriga simulations later on in 
Sec.~\ref{sec:results_FeHRgc}.

@@

\section{Results}
\label{sec:results}
We define GC candidates in the Auriga simulations as all star particles older
than $10$~Gyr based on the age distribution of the MW GCS (top panel of 
Figure~\ref{fig:MW-M31-age-Rgc}), and following \citet{2017MNRAS.465.3622R}.

Troughout our analysis we compare the distributions of three subsets of star
particles: \emph{old stars} (age $>10$~Gyr, or GC candidates), \emph{old in~situ}
stars (defined as those bound to the most-massive halo/subhalo in the first
snapshot that the particle was recorded), and \emph{old accreted} star particles
(those that have formed {\it ex~situ} and are bound to the most-massive halo/subhalo
at $z=0$). For comparison we also include the results for \emph{all stars} (when
no additional selection criterion is applied to the star particles). We consider
the metallicity distribution in Sec.~\ref{sec:results_FeH}, the distribution of
galactocentric radii in Sec.~\ref{sec:results_Rgc}, and the combination of both
in Sec.~\ref{sec:results_FeHRgc}.

\subsection{Metallicity distribution}
\label{sec:results_FeH}
We investigate whether the star formation model implemented in Auriga produces
metallicity distributions consistent with the MW and M31 GC systems, and whether
the simulations generate sufficient total mass at metallicities typical for the
MW and M31 GCS's. To visually inspect the former we show the normalized metallicity 
distribution of three specific Auriga galaxies in Figure~\ref{fig:Au4-10and21_FeH}
in comparison to the MW and M31 [Fe/H] distributions.

\begin{figure*}
    \includegraphics[width=\columnwidth]{{Au4-10_FeH_cleaner-trim}.png}
    \includegraphics[width=\columnwidth]{{Au4-4_and_Au4_21_FeH-trim}.png}
    \caption{
        \emph{Left:} Metallicity distribution of Au4-10 (bottom panel). We show
        the GG candicates in green. We split the GC candidates into two
        subpopulations, those that have formed {\it in~situ} (blue), and those that have
        been accreted (red). The dotted green line shows all star particles.
        The solid purple (magenta) line in the top panel shows the GC system
        of the MW (M31). \emph{Right:} Au4-4 (bottom), and Au4-21 (top).
        \label{fig:Au4-10and21_FeH}
    }
\end{figure*}
We select \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the
resolution level (4) and halo number (10, indicating which set of initial
conditions was used the run).}, \mbox{Au4-21}, and \mbox{Au4-4} to show the
distributions of three individual simulation runs that we consider representative
for specific behaviour, and to highlight that different runs could give rise to 
different distributions. We plot the age-selected GC candidates in green, those
that are accreted in red, and the {\it in~situ} subpopulation in blue. The top 
half of the left figure shows the MW (M31) GC system in purple (magenta), where 
we overplot a double Gaussian for the MW GCS (the purple dashed lines) by 
adopting literature values of the mean $\mu$ and standard deviation $\sigma$ of 
the metal-rich and metal-poor subpopulations \citep[][p. 38]{Harris2001}.

We find that the age cut, on average, lowers the mean metallicity from $0.0$ to
$-0.6$. Furthermore, the old accreted stars generally have lower mean metallicities
than the old {\it in~situ} stars with differences of roughly ${\sim}0.3$ for the majority 
of the simulation runs. This behaviour can be seen in \mbox{Au4-21}, while a 
slightly larger difference of ${\sim}0.5$ dex is seen for \mbox{Au4-10} (as plotted), 
\mbox{Au4-16}, \mbox{Au4-17}, \mbox{Au4-18} and \mbox{Au4-22}. However, this trend 
is reversed for \mbox{Au4-1} and \mbox{Au4-4} for which the old {\it in~situ} population 
has a lower mean metallicity instead. We caution that \mbox{Au4-1} is undergoing
a major merger at redshift zero and note that we find $\mu = -1.51 \, ({-0.74})$ 
for the old {\it in~situ} (accreted) although the former consists of only $1019$ 
particles ($1.3$\% of all GC candidates, and with a total mass of 5e7 M\Sun). 
For \mbox{Au4-4}, ${10.8}$\% of the GC candidates is classified as {\it in~situ} (compared 
to {\it in~situ} fractions of ${40-80}$\% for other haloes). After inspection of
the same figure for every one of the thirty Auriga L4 haloes we find that the 
simulations produce (sub)populations of GC candidates that are more metal-rich
than the MW and M31 GC systems. Moreover, none of the simulations has a 
population of GC candidates with a bimodal metallicity distribution (the green
curves).

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_mu_sigma-trim}.png}
    \caption{
        First vs second central moment of the Auriga L4 metallicity distributions.
        Each cross (for a given colour) represents one simulation. The green (blue)
        [red] crosses show the values calculated using the old (old {\it in~situ})
        [old accreted] star particles. Green triangles indicate that all stars
        were used. The purple (magenta) cross denotes our calculation using all
        MW (M31) observations (which would be appropriate for a unimodal
        distribution). The black solid (open) dots indicate the literature values
        of a bimodal Gaussian fit to the data \citep[values from][p. 38]{1998gcs..book.....A},
        showing the metal-rich (metal-poor) component of the MW.
        \label{fig:FeH_mu_sigma}
    }
\end{figure}

We show the mean metallicity and standard deviation of all thirty Auriga L4 haloes
in Figure~\ref{fig:FeH_mu_sigma} to show the behaviour for the full set of Auriga
galaxies. The green crosses are to be compared to the purple (magenta) cross, 
which shows the mean value of all MW (M31) GCs. In addition, we show the metal-rich 
(metal-poor) population of the MW GCS using a solid (open) dot. We caution that
these literature values result from individual Gaussian fits to sub sets of the 
observational data cut at [Fe/H]~$= -1$. We do not include corresponding data 
points calculated using such an artificial cut for the simulated star particles.
Having said that, we do find it interesting that the mean metallicities of the 
old {\it in~situ} populations appear roughly consistent with that of the metal-rich 
population of the MW although the simulations show larger dispersions. The latter 
could simply be caused by the hard separation of the MW data into two groups, 
which means the range is smaller and the resulting dispersion lower. With 
regard to the M31 GCS, we are uncertain whether definitive consensus is reached
in the literature concerning uni- bi- or trimodality in the [Fe/H] distribution, 
but CR16 argues that the data, after removal of younger objects due to improved 
age classification, hints at three populations separated at [Fe/H]~$>-0.4$ and 
[Fe/H]~$ < 1.5$. None of the Auriga sub sets has a mean value that offers much 
hope that the simulated distribution is consistent with the lowest metallicity 
group in the M31 GCS. This is also true for the metal-poor population of the 
MW with a mean value of $-1.6$. The main take-away from this plot, again, is 
that all Auriga L4 galaxies have metallicity distributions with (much) larger
mean values than what is observed for the MW and M31 GCS, and that we 
systematically find lower mean metallicities for the accreted GC candidates
than for those that have formed {\it in~situ}.

% Finally, we test the null hypothesis that MW (M31) and the GC candidates (all,
% {\it in~situ}, and accreted) are drawn from the same underlying distribution 
% by calculating the KS test statistic (i.e. six KS tests per simulation). We 
% reject $H_0$ at the 100.00~\% confidence level for virtually all subsets of all 
% simulations, both for MW and M31, except when comparing the old accreted stars 
% of \mbox{Au4-10} to the MW GCS. In this case we still reject $H_0$ with, but 
% with $\leq 98.68$~\% confidence. When comparing to the M31 GCS, the `best' 
% matches are the old accreted subpopulations of \mbox{Au4-13}, \mbox{Au4-15}, and 
% \mbox{Au4-17} ($H_0$ rejected with $\leq$ 99.82~\% confidence, 99.95~\%,
% and 98.32~\%). Here we find that the cumulative distributions are more or less
% similar up to [Fe/H]~$-0.5$, above which the simulations yield higher number
% counts which drives the KS test statistic over the critical values. This affirms
% our finding that the simulations produce GC candidates that are more metal-rich
% than the MW (M31) GCS. The main reasons that $H_0$ is rejected with such
% high confidence are under-production of old stars with [Fe/H]~$\leq$~-1.5,
% and over-production of stars with [Fe/H]$\geq$~-0.5.

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and globular cluster candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed {\it in~situ} (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
We now turn to the second goal, which is to see whether sufficient total mass in 
GC candidates is produced by the Auriga simulations. To answer this question we plot
a mass-weighted metallicity distribution in Figure~\ref{fig:FeH}. We show the 
median (coloured lines) for all thirty Auriga L4 haloes with the $1\sigma$ 
interval around it (shaded regions, which shows the scatter between runs that 
have different initial conditions, thus, have unique merger histories). We chose 
to aggregate the data to indicate general trends that we find when the GC candidates 
are split up according to birth location, rather than selecting typical examples 
of individual (simulated) galaxies. Once again we notice that the peak metallicity 
shifts down from $0$ to $-0.6$ for old stars (green solid) compared to all stars 
(green dotted), and we learn that the mass at the peak lowers by roughly one dex. 
The mass budget of the old stars is dominated by the old {\it in~situ} population (blue 
solid) below [Fe/H]~=~$-1$, and by the old accreted stars (red solid) above this 
value. We show the MW (M31) GCS in purple (magenta) and notice that the difference 
between the MW and M31 distributions is substantially larger than the scatter
between different Auriga galaxies, particularly around [Fe/H]~$=-1$. In addition, 
Andromeda does host (a hand full) GCs with [Fe/H]~$< -2.5$ as well as GCs with 
[Fe/H]~$ > 0$ while the Milky Way does not.

We show the ratio of the  simulated to the observed profiles in the middle (bottom) 
panel. This mass excess can be thought of the `mass budget' that the Auriga GC 
candidates can `afford to lose' due to a combination of smaller than unity bound
cluster formation efficiencies combined with a Hubble time of dynamical evolution,
while still producing sufficient mass at the right metallicities. In particular,
the cluster formation efficiency would have to decrease with decreasing 
metallicity for Auriga GC candidates to produce a population of GC candidates 
that is consistent with the MW. For the GC candidates in M31 we find a constant 
mass excess up to $-0.9$, above which the simulations produce a higher mass excess 
with increasing metallicity. If dynamical evolution is not expected to more 
efficiently disrupt GCs of higher metallicity, then we would find that the 
efficiency to form bound star clusters would have to decrease with increasing 
metallicity.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{LogRgc_mu_sigma-trim}.png}
    \caption{
        Mean and standard deviation of the logarithm of radial distribution 
        of star particles in each of the thirty Auriga L4 haloes compared to
        the MW (M31) GCS shown in purple (magenta).
        \label{fig:Rgc_mu_sigma}
    }
\end{figure}
We repeat the analysis of the previous subsection for the distribution of
galactocentric radius instead of metallicity. We look for general trends present
in all Auriga L4 galaxies. Figure~\ref{fig:Rgc_mu_sigma} shows the mean and 
standard deviation of $\log_{10}(R_{\text{GC}})$ of star particles in all Auriga
L4 simulations. The purple (magenta) cross again shows the mean of the MW (M31)
GCs (which are to be compared to the green crosses), but solid (open) dot now
shows our calculation of the mean value of the metal-rich (metal-poor) population 
as no literature values were available. We split the radii up into the 
metal-rich/metal-poor groups by taking a metallicity cut at [Fe/H]~=~-1 as is 
done in the literature.

We notice that the old {\it in~situ} populations are more centrally 
distributed, whereas the old accreted subsets have a larger radial extent. This 
is not surprising because the classification of {\it in~situ} requires star particles 
to have formed within the virial radius, thus they could naturally be expected 
to end up at small galactocentric radii. Accreted star particles, on the other 
hand, have formed in another (sub)halo beyond the virial radius, thus, would 
first have to migrate inwards in order to populate the innermost radii. Moreover,
we find that the simulations have a wider dispersion in $\log(R_{\text{GC}}$ than
the MW GCS, while the dispersion of M31 seems to lie witin the range of dispersions
found in the Auriga galaxies. Furthermore, the mean of the MW GCS lies roughly 
within the range of values produced by the Auriga simulations, whereas the mean 
of M31 is somewhat larger and slightly closer to typical mean values of the 
accreted GC candidates in the Auriga simulations. The larger radial extent 
of the M31 GCS is generally believed to hint at a more accretion-dominated origin 
of the GCS, and may reflect a richer accretion history of the galaxy in comparison 
to the Milky Way.
